On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement

### 2023-10-17 manuscript/manuscript.tex
manuscript: final literature items and formatting
manuscript: internal revision

\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\set}[1]{\left\{#1\right\} }
\DeclareMathOperator*{\argmin}{\arg\!\min}
\newcommand{\R}{\mathbb{R} }
\newcommand{\B}{\mathbb{B} }
\newcommand{\N}{\mathbb{N} }
\newcommand{\co}{\ce{CO2}~}
\def\el{${}_{\textrm{el}}$}
\def\th{${}_{\textrm{th}}$}
\def\deg{${}^\circ$}

@@

	\title{On the means, costs, and system-level impacts of the 24/7 carbon-free energy procurement}

@@

All code, input data and results are published under an open license. The code to reproduce the experiments is available at GitHub: \href{https://github.com/Irieo/247-procurement-paper}{github.com/Irieo/247-procurement-paper}.

>>>>

\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\set}[1]{\left\{#1\right\} }
\DeclareMathOperator*{\argmin}{\arg\!\min}
\newcommand{\R}{\mathbb{R} }
\newcommand{\B}{\mathbb{B} }
\newcommand{\N}{\mathbb{N} }
\newcommand{\co}{\ce{CO2}}
\def\el{${}_{\textrm{el}}$}
\def\th{${}_{\textrm{th}}$}
\def\deg{${}^\circ$}

@@

	\title{On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement}

@@

All code, input data and results are published under an open license. The code to reproduce the experiments is available at GitHub \cite{github-247CFEpaper}.

### 2023-10-17 manuscript/sections/abstract.tex
manuscript: title, keywords, and final touches main text
manuscript: internal revision

% The 5 things a good abstract needs:

% 1. Introduce the topic: what we know 
% 2. State the unknown: what we don't know
% 3. Outline the methods: how we answer the questions
% 4. Preview the findings: what we learned
% 5. Tell us what your work teaches us: what we conclude and why this is important

% aim ~200 words | 225 words used

A growing number of public and private energy buyers are interested in 24/7 carbon-free energy (CFE) procurement, which means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
It has the potential to overcome the limitations of established procurement schemes, such as the temporal mismatch between clean electricity supply and buyers' demand that is inherent to "volumetric" matching. 
Yet it is unclear whether 24/7 CFE procurement is only effective during the early stages of the energy transition, or if it has a system-level impact in a variety of regional contexts.
We use a mathematical model to systematically examine different designs, optimal procurement strategies, costs, and impacts of the 24/7 CFE matching, both for participating buyers and for regions where voluntary procurement occurs.
We examine the mechanisms driving system-level co emissions reduction and how they vary across regions and over time.
Our results indicate that voluntary clean energy procurement commitments have consistent effects on participants and the electricity system.
Even as grids become cleaner over time, the hourly matching strategy remains significant in reducing CO$_2$ emissions.
In addition, voluntary commitments to 24/7 CFE have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
This work generalises the implications of clean energy procurement strategies in the context of evolving national energy and climate policies.

>>>>

% The 5 things a good abstract needs:
% 1. Introduce the topic: what we know 
% 2. State the unknown: what we don't know
% 3. Outline the methods: how we answer the questions
% 4. Preview the findings: what we learned
% 5. Tell us what your work teaches us: what we conclude and why this is important
% aim ~200 words | 225 words used
A growing number of public and private energy buyers are interested in 24/7 carbon-free energy (CFE) procurement, which means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
It has the potential to overcome the limitations of established procurement schemes, such as the temporal mismatch between clean electricity supply and buyers' demand that is inherent to \enquote{volumetric} matching. 
Yet it is unclear how 24/7 CFE procurement affects the rest of the power system, and whether this effect is consistent across regional contexts and different levels of system cleanness.
We use a mathematical model to systematically examine different designs, optimal procurement strategies, costs, and impacts of the 24/7 CFE matching, both for participating buyers and for regions where voluntary procurement occurs.
We examine mechanisms driving system-level emissions reduction and how they vary across regions and over time.
Our results indicate that clean energy procurement commitments have consistent beneficial effects on participants and the electricity system.
Even as grids become cleaner over time, the hourly matching strategy contributes significantly to system-level emissions reduction.
In addition, voluntary commitments to 24/7 CFE have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.

### 2023-10-17 manuscript/sections/discussion.tex
manuscript: internal revision

% Where we converge: on advanced technologies
Another important finding of this work that confirms prevailing understanding is that 24/7 CFE matching creates an early market for advanced energy technologies. Citing an episode of the David Roberts' Volts podcast: \enquote{One reason energy nerds are excited about the 24/7 trend is that it's going to pull forward in time a bunch of questions (and investment decisions) that were going to face grids trying to reach 100 percent CFE anyway} \cite{roberts-intro247CFE}. Further research is needed to better understand how 24/7 CFE commitments push advanced energy technologies along their learning curves, and to estimate the potential economic impact on global decarbonisation costs.

@@

% Where we add: Decarbonisation story
A deeper look at the role of voluntary clean energy procurement commitments in grid decarbonisation reveals that the hourly matching strategy retains its significance in reducing system-level emissions, even as grids become cleaner over time.
We examined two distinct mechanisms through which 24/7 CFE procurement facilitates system decarbonization: "profile" and "volume".
As companies adapt their procurement strategies, it is important to understand how these mechanisms perform across different grid locations and years.
Interestingly, the disparity between the annual renewable (\enquote{volumentric}) matching and 24/7 CFE hourly matching strategies in decarbonisation outcomes becomes ever more evident as electricity grids become cleaner.
This phenomenon illustrates the effectiveness of 24/7 CFE procurement in supporting system decarbonisation within the context of evolving national energy and climate policies.

@@

%Limitations: electricity sector only
First, only the electricity sector is included in the mathematical model of the European energy system.
The research focus of this study justifies it.
However, it is important to acknowledge that the electricity sector is not an isolated system, but it is closely linked with other energy sectors, such as heat and transport.
Brown et al. (2018) discuss the synergies of sector coupling in the integrated European energy system \cite{brownSynergiesSectorCoupling2018}.

@@

% Excess constraint problem
One of the simplifications of mathematical models implementing 24/7 CFE procurement is how the excess carbon-free electricity is handled. 
The \enquote{excess CFE} can be defined as the total amount of carbon-free electricity supply exceeding the demand of the participating consumers in a given period of time.
Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices, until the excess constraint is reached (see \cref{sec:si_3} for detail).
The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement. 
Similar \enquote{spillover effect} problem has been observed and discussed by Xu et al. (2022) \cite{xu-247CFE-SSRN}.
In their white paper, Peninsula Clean Energy team also discuss the problems and implications of the excess supply. Citing their work: \enquote{We conclude that excess supply is a necessary aspect of a time-coincident renewable portfolio in the range of likely market conditions in California today} \cite{peninsula-report247}.
Both studies perform sensitivity analyses on the excess supply and discuss the implications on their findings \cite{xu-247CFE-SSRN, peninsula-report247}.

% On "emissionality" approach
\textbf{Is 24/7~CFE the right strategy? --} Last but not least, it is worth mentioning an ongoing discussion whether 24/7 CFE is the right strategy for companies to reduce their carbon emissions.
Some proponents of alternative strategies contend that 24/7 CFE, or \enquote{temporal matching}, may not represent the most effective approach to emissions reduction. 
Instead, they suggest that companies, in their pursuit to reduce system-level carbon emissions, should focus on system-wide impact as measured via short-run marginal emissions accounting (\enquote{emissions matching}).
This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover 24/7 consumption will be different from optimising the assets to \enquote{offset emissions} based on the short-run marginal emission estimates of the grid.
Xu~et~al. (2023) bring this discussion from the realm of arguments into quantitative analysis, discovering that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level \co emissions} \cite{princeton-247CFEvsEmissionality}.

>>>>

% Where we converge: on advanced technologies
Another important finding of this work that confirms prevailing understanding is that 24/7 CFE matching creates an early market for advanced energy technologies. Further research is needed to better understand how 24/7 CFE commitments push advanced energy technologies along their learning curves, and to estimate the potential economic impact on global decarbonisation costs.

@@

% Where we add: Decarbonisation story
A deeper look at the role of voluntary clean energy procurement commitments in grid decarbonisation reveals that the hourly matching strategy retains its significance in reducing system-level emissions, even as grids become cleaner over time.
We examined two distinct mechanisms through which 24/7 CFE procurement facilitates system decarbonization: \enquote{profile} and \enquote{volume}.
As companies adapt their procurement strategies, it is important to understand how these mechanisms perform across different grid locations and years.
Interestingly, the disparity between the annual renewable (\enquote{volumentric}) matching and 24/7 CFE hourly matching strategies in decarbonisation outcomes becomes ever more evident as electricity grids become cleaner.
This phenomenon illustrates the effectiveness of 24/7 CFE procurement in supporting system decarbonisation within the context of evolving national energy and climate policies.

@@

%Limitations: electricity sector only
First, only the electricity sector is included in the mathematical model of the European energy system, which is justified by the research focus.
However, it is important to acknowledge that the electricity sector is not an isolated system, but is increasingly becoming linked with other energy sectors, such as heat and transport.
Brown et al. (2018) discuss the synergies of sector coupling in the integrated European energy system \cite{brownSynergiesSectorCoupling2018}.

@@

% Excess constraint problem
One of the simplifications of mathematical models implementing 24/7 CFE procurement is how the excess carbon-free electricity is handled. 
The \enquote{excess CFE} can be defined as the total amount of carbon-free electricity supply exceeding the demand of the participating consumers in a given period of time.
Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices, until the excess constraint is reached (see \cref{sec:si_3} for detail).
The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement; and if system-wide renewable expansion is constrained, the cost-optimal solution may be to use the excess CFE to \enquote{relax} the constraint, increasing the renewable portfolio of participating consumers.
Similar \enquote{spillover effect} problem has been observed and discussed by Xu et al. (2022) \cite{xu-247CFE-SSRN}.
In their white paper, Peninsula Clean Energy team also discuss the problems and implications of the excess supply. Citing their work: \enquote{We conclude that excess supply is a necessary aspect of a time-coincident renewable portfolio in the range of likely market conditions in California today} \cite{peninsula-report247}.
Both studies perform sensitivity analyses on the excess supply and discuss the implications on their findings \cite{xu-247CFE-SSRN, peninsula-report247}.

% On "emissionality" approach
\textbf{Is 24/7~CFE the right strategy? --} Last but not least, it is worth mentioning an ongoing discussion whether 24/7 CFE is the right strategy for companies to reduce their carbon emissions.
Some proponents of alternative strategies contend that 24/7 CFE, or \enquote{temporal matching}, may not represent the most effective approach to emissions reduction. 
This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover own consumption 24/7 with clean electricity is a different strategy to optimising the assets specifically to displace \enquote{as much emissions as possible}.

One of the alternative strategies could be that companies, in their pursuit to reduce system-level carbon emissions, focus on system-wide impact as measured via short-run marginal emissions accounting (\enquote{emissions matching}).
Xu~et~al. (2023) bring this discussion from the realm of arguments into quantitative analysis, concluding that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level \co emissions} \cite{princeton-247CFEvsEmissionality}.

Another alternative strategy could be that companies do annual matching with \enquote{overprocurement}, i.e., covering own consumption on an annual volumentric basis plus procuring some more clean electricity on top. Such strategy could be implemented at low cost, e.g., with solar PV. 
However, as shown in \cref{subsec:mechanisms}, this strategy would not be as effective in reducing system-level emissions as 24/7 CFE matching, especially in the context of evolving national energy and climate policies.  
Further, such a strategy would not promote innovation and pull forward in time research and investment decisions in advanced energy technologies, such as long-duration energy storage and clean firm generators.

### 2023-10-17 manuscript/sections/introduction.tex
manuscript: internal revision

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
The European Union (\gls{eu}) has committed to achieve net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}. 
National climate initiatives span the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have \co emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.

@@

Many public and private energy buyers join this effort by purchasing clean energy to demonstrate their sustainability credentials. The established schemes for voluntary clean energy procurement are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (\gls{rec}s) in the United States.
A common feature of these schemes is that renewable energy credits are \enquote{unbundled} from megawatt-hours of energy and can be traded numerous times on specialized markets before being retired.
The owner gets to claim environmental benefits when \enquote{retiring} (i.e. using) the certificate.
The unbundled renewable energy credits, however, have been criticized for not ensuring a physical match between renewable energy generation and consumption, and for absence of evidence that such schemes drive build-out of additional renewable energy capacity \cite{bjorn-RECSnatcom-2022, gillenwater-2014, re100report-2020, spglobal-recs, bock-icelandGOproblem}.

@@

\textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demands.
As an example, more than 400 members of the RE100 group \cite{re100report-2020} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
Even the \enquote{best case} of the 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem -- the temporal mismatch between renewable energy supply and electricity demand.
In hours when wind and solar generation is low, energy buyers have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyers portfolio.
Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.

@@

\textbf{Proposed solution: 24/7 CFE --} There is growing interest from the leaders in the clean energy procurement to move beyond the 100\% annual matching approach.
The next frontier in the clean energy procurement is the 24/7 Carbon-Free Energy (\gls{cfe}) procurement, which aims to match clean energy supply with electricity demand on an \textit{hourly basis}.
Thus, 24/7~CFE procurement has the potential to eliminate all greenhouse gas emissions associated with electricity use of the parciticpating companies.
Furthermore, 24/7~CFE procurement is focused on \textit{carbon-free} rather than renewable energy, which opens up opportunities for a broad range of advanced energy technologies, such as long-duration energy storage (\gls{ldes}) or new clean firm power generators that are needed for deep decarbonisation of the energy systems.

Google broke the 24/7 ground in 2020 by announcing its commitment to entirely on the 24/7~CFE approach at all its data centres and campuses worldwide by 2030 \cite{google-247by2030}.
Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}. 
The list of entities that have committed to 24/7~CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}. In 2021, an international group of energy suppliers, buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact \cite{gocarbonfree247}.
With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all}.

@@

\textbf{Existing literature on 24/7 CFE --} The growing interest in the means, costs and the system-level impacts of hourly \gls{cfe} procurement created a need for a quantitative analysis of the approach.
The existing model-based studies on 24/7~CFE approach are very recent.
The first to incorporate it into the electricity system planning model were Xu et al. (2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior report published in November 2021 investigating the system-level impacts of 24/7~CFE in two regions of the U.S. -- California and PJM \cite{xu-247CFE-report}.} 
The authors study the system-level impacts of 24/7~CFE procurement based on an example of California in the year 2030.
In November 2022, IEA also released a model-based study on the 24/7~CFE, focusing on India and Indonesia \cite{ieaAdvancingDecarbonisationClean2022}.
In early 2023, Peninsula Clean Energy published an own white paper introducing their modeling tool---MATCH (Matching Around-the-Clock Hourly energy)---and the results of the modeling indicating feasibility of the company's \enquote{24/7 renewable energy by 2025} goal \cite{peninsula-report247}.

@@

\textbf{Contribution --} The goal of this work is to systematically explore different designs, optimal procurement strategies, costs, benefits and impacts of the 24/7~CFE matching approach, both for participating buyers and for regions where voluntary procurement occurs.
Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
Additionally, we examine the underlying mechanisms that drive the system-level reduction of \co emissions, and examine how they perform over time and across regions. 
This work is a follow-up to the earlier public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.

>>>>

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
The European Union (\gls{eu}) has committed to achieving net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}. 
National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have \co emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.

@@

Many public and private energy buyers have joined this effort by purchasing clean energy to demonstrate their sustainability credentials. 
The established certification schemes for voluntary clean energy procurement are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (\gls{rec}s) in the United States.
A common feature of these schemes is that renewable energy credits are \enquote{unbundled} from megawatt-hours of energy and can be traded numerous times on specialized markets before being retired.
The owner gets to claim environmental benefits when \enquote{retiring} (i.e. using) the certificate.
The unbundled renewable energy credits, however, have been criticized for not ensuring a physical match between renewable energy generation and consumption \cite{spglobal-recs, bock-icelandGOproblem, re100report-2020}, and for absence of evidence that such schemes drive build-out of additional renewable energy capacity \cite{bjorn-RECSnatcom-2022, gillenwater-2014}.

@@

\textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demand.
As an example, more than 400 members of the RE100 group \cite{re100report-2020} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
Even the \enquote{best case} of 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem: the temporal mismatch between renewable energy supply and electricity demand.
In hours when wind and solar generation is low, energy buyers have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyer's portfolio.
Furthermore, the 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.

@@

\textbf{One proposed solution: 24/7 CFE --} There is growing interest from the leaders in the clean energy procurement to move beyond the 100\% annual matching approach.
One approach is called 24/7 Carbon-Free Energy (\gls{cfe}) procurement, which aims to match clean energy supply with electricity demand on an \textit{hourly basis}.
Thus, 24/7~CFE procurement has the potential to eliminate all greenhouse gas emissions associated with electricity use of the participating companies.
Furthermore, 24/7~CFE procurement is focused on \textit{carbon-free} rather than renewable energy, which opens up opportunities for a broad range of advanced energy technologies, such as long-duration energy storage (\gls{ldes}) or new clean firm power generators that are needed for deep decarbonisation of energy systems.

Google led the 24/7 movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}. 
The list of entities that have committed to 24/7 CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}. In 2021, an international group of energy suppliers, electricity buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact \cite{gocarbonfree247}.
With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all}.

@@

\textbf{Existing literature on 24/7 CFE --} The growing interest in the means, costs and the system-level impacts of hourly \gls{cfe} procurement has created a need for a quantitative analysis of the approach.
There is relatively little research on the system-level impacts of 24/7~CFE procurement; and it is all fairly recent.
The first to incorporate it into the electricity system planning model were Xu et al. (2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior report published in November 2021 investigating the system-level impacts of 24/7~CFE in two regions of the U.S. -- California and PJM \cite{xu-247CFE-report}.} 
The authors study the system-level impacts of 24/7~CFE procurement based on an example of California in the year 2030.
In November 2022, IEA also released a model-based study on the 24/7~CFE, focusing on India and Indonesia \cite{ieaAdvancingDecarbonisationClean2022}.
In early 2023, Peninsula Clean Energy published an own white paper introducing their modeling tool---MATCH (Matching Around-the-Clock Hourly energy)---and the results of the modeling indicating feasibility of the company's \enquote{24/7 renewable energy by 2025} goal \cite{peninsula-report247}.

@@

\textbf{Contribution --} The novelty of this study is to go beyond case studies and show in a systematic way, across many regions and levels of energy transition, how voluntary commitments to 24/7 CFE procurement impact participating buyers and regions where voluntary procurement occurs.
We explore different designs, optimal procurement strategies, costs, benefits and system-level impacts of the 24/7~CFE matching approach.
Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
Additionally, we examine the underlying mechanisms that drive the system-level reduction of \co emissions, and examine how they perform over time and across regions. 
This work is a follow-up to the earlier public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.

### 2023-10-17 manuscript/sections/methods.tex
manuscript: internal revision

The modelling workflow is based on the PyPSA --- an open-source software framework for simulating and optimising modern energy systems \cite{brownPyPSAPythonPower2018}.

\textbf{Optimisation model --} The simulations were carried out with the modified version of the PyPSA-Eur model \cite{PyPSA-Eur-github}. 
The objective of the model is to minimise the annualised system-wide costs of meeting energy demand within the modelled system, while adhering to all relevant engineering, reliability, and policy constraints.
We use a brownfield investment approach, which means that we keep the existing power generation and storage assets in the model and only optimise the capacity expansion of new assets.
The optimal solution of the model includes the location and capacity of new power generation and storage assets, as well as the hourly dispatch of all existing and new assets, including the linear optimal power flow on the transmission network for the planning year. 
This is standard for the PyPSA-Eur model \cite{horschPyPSAEurOpenOptimisation2018} and the long-term energy planning models of this class \cite{jenkinsGenX2022, howellsOSeMOSYSOpenSource2011}.

@@

The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google (2021) \cite{google-methodologies}.
The framework considers various \gls{cfe} supply options for the participating consumers, including procurement of own generation resources and storage assets, and electricity imports from the local grid.
The framework also allows for controlling \textit{the quality score} of the 24/7~CFE procurement by setting the target threshold for the minimum share of hours when the hourly \gls{cfe} supply meets the hourly electricity demand.
The quality score is hereinafter referred to as \enquote{CFE target}, which takes values in percent points, e.g., 95\%, 99\%, 100\%.
The higher the CFE target, the higher the quality of the 24/7~CFE supply; see equation [TODO] for details.

@@

We model two individual years: 2025 and 2030. 
From a modelling perspective, a five-year step changes many system parameters.
In particular, technology costs decline as a result of economies of scale and incremental innovation, \gls{necp}s become tighter, and some legacy power plants go out of business.
The problem is solved with a temporal resolution of 2920 snapshots, representing a 3-hourly average of the hourly time-series data.

@@

\begin{itemize}[-]
    \item \textit{100\% annual matching}: participating buyers meet their annual energy demand on volumetric basis with additional renewable energy procurement;
    \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality target.
\end{itemize}

We setup the study design so that the procurement strategies are modelled under the same conditions.
In both cases (i) procurement is possible with generators from the same bidding zone only (i.e., we model the \enquote{best case} of the annual matching strategy); (ii) the same set of consumers participate; (iii) the same set of constraints is applied to the rest of the electricity system. 
For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and purchase all their electricity from the local grid.

@@

\begin{itemize}[-]
    \item \textit{Palette 1} -- technologies that are commercially available today: onshore wind, utility scale solar photovoltaics (\gls{PV}), and battery storage;
    \item \textit{Palette 2} -- all above plus a long-duration energy storage (\gls{ldes}) that is expected to be commercially available in the near future; 
    \item \textit{Palette 3} -- all above plus promising advanced technologies that are in prototype stage today, but are expected to be commercially available in the future: Allam cycle power plant with \gls{ccs}\footnote{Allam cycle is a natural gas power plant with up to 100\% of carbon capture and sequestration}, and advanced dispatchable generators -- a stand-in for clean firm technologies, such as advanced geothermal or advanced nuclear systems.
\end{itemize}

\textbf{Technology assumptions --} Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in [\cref{tab:tech_costs}].
For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion. 
Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, use own indicative assumptions.

>>>>

\textbf{Optimisation model --} The simulations were carried out with the modified version of the open European power system model PyPSA-Eur, built using the open framework PyPSA \cite{brownPyPSAPythonPower2018}.
The objective of the model is to minimise the annualised system-wide costs of meeting energy demand within the modelled system, while adhering to all relevant engineering, reliability, and policy constraints.
We use a brownfield investment approach, which means that we keep the existing power generation and storage assets in the model and only optimise the capacity expansion of new assets.
The optimal solution of the model includes the location and capacity of new power generation and storage assets, as well as the hourly dispatch of all existing and new assets, including the linear optimal power flow on the transmission network for the planning year. 
This is standard for the PyPSA-Eur model \cite{horschPyPSAEurOpenOptimisation2018} and the long-term energy planning models of this class \cite{jenkinsGenX2022, howellsOSeMOSYSOpenSource2011}.

@@

The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google (2021) \cite{google-methodologies}.
The framework considers various \gls{cfe} supply options for the participating consumers, including procurement of their own generation resources and storage assets, and electricity imports from the local grid.
The framework also allows for controlling \textit{the quality score} of the 24/7~CFE procurement by setting the target threshold for the minimum share of hours when the hourly \gls{cfe} supply meets the hourly electricity demand.
The quality score is hereinafter referred to as the \enquote{CFE target}, which takes values in percent points, e.g., 95\%, 99\%, 100\%.
The higher the CFE target, the higher the quality of the 24/7~CFE supply; see equation [TODO] for details.

@@

We model two individual years: 2025 and 2030. 
From a modelling perspective, a five-year step changes many system parameters.
In particular, technology costs decline as a result of economies of scale and incremental innovation, \gls{necp}s become tighter, \co prices increase, and some legacy power plants go out of business.
The problem is solved with a temporal resolution of 2920 snapshots, representing a 3-hourly average of the hourly time-series data.

@@

\begin{itemize}[-]
    \item \textit{100\% annual matching}: participating buyers meet their energy demand on an annual volumetric basis with additional renewable energy procurement;
    \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality target.
\end{itemize}

We set up the study design so that the procurement strategies are modelled under the same conditions.
In both cases (i) procurement is only possible with generators from the same bidding zone (i.e., we model the \enquote{best case} of the annual matching strategy); (ii) the same set of consumers participate; (iii) the same set of constraints is applied to the rest of the electricity system. 
For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and purchase all their electricity from the local grid.

@@

\begin{itemize}[-]
    \item \textit{Palette 1} -- technologies that are commercially available today: onshore wind, utility scale solar photovoltaics (\gls{PV}), and battery storage;
    \item \textit{Palette 2} -- all above plus a long-duration energy storage (\gls{ldes}) that is expected to be commercially available in the near future; 
    \item \textit{Palette 3} -- all above plus promising advanced technologies that are in prototype stage today, but are expected to be commercially available in the future: (i) Allam cycle power plant with \gls{ccs}\footnote{Allam cycle is a natural gas power plant with up to 100\% of carbon capture and sequestration} to represent a technology option with higher operational expences (\gls{opex}), and (ii) \enquote{an advanced dispatchable generator}, a stand-in for clean firm technologies with higher capital expences (\gls{capex}), such as advanced geothermal or nuclear systems.
\end{itemize}

\textbf{Technology assumptions --} Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in [\cref{tab:tech_costs}].
For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion. 
Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, use our own indicative assumptions.
